### 2022-01-10 abstract.tex
fixing

\begin{abstract}
    \todo[inline]{TODO}
\end{abstract}

>>>>

\begin{abstract}
    \acfp*{NCS} have long been a subject of theoretical research, however, little work has been devoted to repeatable and scalable experimentation.
    The advent of edge computing and the subsequent proliferation of \acsp*{NCS} has quickly led this to become a key issue that needs to be addressed.

    In this work, we present a novel, completely software-based approach to this challenge.
    Our core idea rests on a framework for the emulation of physical plants which communicate with controllers implemented in software over a real network.
    This approach is furthermore designed and built for the Edge, using a general-purpose programming language and will full compatibility with industry-standard containerization solutions.
    We validate this framework using an initial implementation of an inverted pendulum \acs*{NCS}.
    Our results showcase the utility of the tool as a repeatable, extensible, and scalable solution to \acs*{NCS} performance evaluation.
\end{abstract}

### 2022-01-10 cleave.tex
fixing

In this section, we present and detail our \ac{CLEAVE} framework for the performance evaluation of \acfp{NCS}, with a particular focus on edge deployments.
The framework is distributed as \emph{free and open-source} software, and can be found online in the \emph{GitHub} organization of the \emph{KTH ExPECA} research group\footnote{\url{https://github.com/KTH-EXPECA/CLEAVE}}.
Our design follows an approach similar to the above-discussed \emph{hardware-in-the-loop} setups, in that we provide a \emph{framework} for the real-time \emph{emulation} of physical control systems which interact with \emph{real} networks.
This allows for great flexibility when it comes to the components of the control system, as these can easily be switched out in the fully emulated approach, while maintaining the realism of arguably the most complex and limiting component of and edge \acp{NCS}, namely the network itself.

@@

For the purpose of this work, we have used \ac{CLEAVE} to implement an emulated \emph{inverted pendulum} control loop; see \cref{fig:invpend}.
We have chosen this system as an initial benchmark for its relative simplicity as well as prevalence in the field of automatic control as one of the fundamental examples of linear control.
However, we eventually plan to build an open library of emulated control loops.

>>>>

In this section, we present and detail our \ac{CLEAVE} framework for the performance evaluation of \acfp{NCS}, with a particular focus on edge deployments.
The framework is distributed as \emph{free and open-source} software, and can be found online in the \emph{GitHub} organization of the \emph{KTH ExPECA} research group\footnote{\url{https://github.com/KTH-EXPECA/CLEAVE}}.
Our design follows a virtualized emulation approach; we provide a \emph{framework} for the real-time \emph{emulation} of physical control systems which interact with \emph{real} networks.
This allows for great flexibility when it comes to the components of the control system, as these can easily be switched out in the fully emulated approach, while maintaining the realism of arguably the most complex and limiting component of and edge \acp{NCS}, namely the network itself.
In other words, \ac{CLEAVE} is a platform with an easy-to-use \ac{API} on which a multitude of \ac{NCS} types can be emulated.
Our vision is to furthermore provide an open library of \ac{NCS} implementations in the future, this way making the tool even more accessible to the community.

@@

For the purpose of this work, we have used \ac{CLEAVE} to implement an emulated \emph{inverted pendulum} control loop; see \cref{fig:invpend}.
We have chosen this system as an initial benchmark for its relative simplicity as well as prevalence in the field of automatic control as one of the fundamental examples of linear control.
However, as mentioned above, we eventually plan to build an open library of emulated control loops.

### 2022-01-10 conclusion.tex
fixing

In this work, we aim to tackle this issue by presenting a fully software-based framework for repeatable, reproducible, and easily scalable \ac{NCS} benchmarking with a particular focus on edge deployment.
Our framework, \ac{CLEAVE}, is fully parametrizable and built with industry-standard edge technologies and paradigms in mind.
We validate the utility of this tool through a series of scenarios, from which we are able to extract relevant metrics relating to the stability of the control system, as well as on the perfomance of the underlying network link.
\todo[inline]{Talk a bit more about results?}
We believe \ac{CLEAVE} represents an important step towards enabling inexpensive and low-complexity scalable research for real-world deployment of edge-bound \acp{NCS}.

>>>>

In this work, we aim to tackle this issue by presenting a fully software-based framework for repeatable, reproducible, and easily scalable \ac{NCS} benchmarking with a particular focus on edge deployment.
Our framework, \ac{CLEAVE}, is fully parametrizable, extendable, and built with industry-standard edge technologies and paradigms in mind.
We validate the utility of this tool through a series of scenarios; our results showcase the ability of the framework to extract relevant metrics relating to the stability of the control system, as well as on the perfomance of the underlying network link.
We believe \ac{CLEAVE} represents an important step towards enabling inexpensive and low-complexity scalable research for real-world deployment of edge-bound \acp{NCS}.

### 2022-01-10 experiments.tex
fixing

We repeat each combination of these parameters at least \num{10} times, for both the networked and ``local-only'' setups; experiments with interesting and relevant results are then repeated an additional \num{20} times for better statistical significance in the results.
\todo[inline]{Explain criteria for repeated experiments? Or just drop this sentence?}
Each repetition lasts for \SI{5}{\minute}, during which we collect detailed data on both the state of the controlled system as well as on the data sent over the network.

>>>>

We repeat each combination of these parameters at least \num{10} times, for both the networked and ``local-only'' setups; experiments with sampling rates \( \geq \) \SI{20}{\hertz} and artificial delays \( \geq \) \SI{25}{\milli\second} where repeated an additional \num{20} times for better statistical significance.
Each repetition lasts for \SI{5}{\minute}, during which we collect detailed data on both the state of the controlled system as well as on the data sent over the network.

### 2022-01-10 intro.tex
fixing

The number and applications of \acp{CPS}~\cite{Rajkumar2010CPS} --- that is, systems in which a real, physical mechanism is controlled by a computer --- have exploded in recent years.
However, this rapid increase in adoption of these systems has been mostly limited to industrial contexts.
Although \acp{CPS} present huge opportunities for all facets of society, they have yet to reach our daily lives in any relevant scale due to their stringent operational requirements.
This is about to change, however, as with the advent of novel wireless communication technologies as well as networking paradigms, such as cellular 5G and Edge (and Fog) Computing~\cite{Satya2017Emergence}, consumer-grade \acp{CPS} will be made possible.
These technologies meet two key requirements of \acp{CPS}: real-time capabilities (through extremely low end-to-end latencies), and context- and locality-awareness, and will most likely become the backbone of \ac{CPS} in the future.

@@

Due to their potential advantages for industrial and commercial settings, a large body of work exists dedicated to the modelling and performance characterization of \aclp{NCS}~\cite{Zhang2013Survey,Zhang2016Survey}.
\Acp{NCS} enhance the flexibility of and improve existing control systems by allowing for the distribution of control functions over and across networks.
This allows for, for instance, simultaneous centralized coordination, control, and monitoring of potentially hundreds of devices.

@@

One approach to experimental research in \acp{NCS} uses setups in which the complete system is built on top of real hardware.
This approach is employed in the works of, for instance, \textcite{Li2014Wireless,Baumann2018LowPower,Cuenca2019UAV}; in all of these, the authors implement and validate their results on physical testbeds of different kinds.
Conversely, some studies choose to instead use completely \emph{simulated} \ac{NCS} setups.
\textcite{Wu2012NPC,Chen2015synccontrol,Ma2019DynamicSched} are examples of works in which the authors have opted for such completely virtualized approaches.
These studies often employ combinations of physical and network simulation libraries to try to capture the complex dynamics of \acp{NCS}.
Finally, a number of experimental studies instead employ \emph{hardware-} and \emph{network-in-the-loop} approaches.
Hardware-in-the-loop refers to \ac{NCS} setups in which a real network interacts with a simulated or emulated control system~\cite{Wang2020VoltageControl}.
On the other hand, network-in-the-loop refers to experimental setups in which the \emph{network} is instead simulated or emulated~\cite{Natale2004InvPendEthernet}.

As evidenced above, experimental research in \acp{NCS} includes a large variety of heterogeneous hardware and software platforms, as well as methodologies and \acp{KPI}.
This, in turn, leads to hardware, software, and methodology fragmentation, as different studies tend to prefer approaches more favored in their respective communities.
Furthermore, existing studies tend to focus on individual aspects and components of a system, thus producing results which do not provide a complete image of the \ac{NCS}.
This has caused a gap in knowledge pertaining to the reproducibility and comparison of experimental studies on these systems.

\textcite{Zoppi2020NCSBench} made the first (and to the best of our knowledge, the only) attempt at tackling this challenge with their \emph{NCSbench} platform.
\emph{NCSbench} is an open-source \ac{NCS} benchmarking platform designed with reproducibility in mind, built on top of the LEGO\textregistered{}\ Mindstorms EV3 Core Set\texttrademark{}\ platform\footnote{\url{https://education.lego.com/en-us/products/lego-mindstorms-education-ev3-core-set/5003400\#lego-mindstorms-education-ev3}}.
It allows for easy and highly reproducible benchmarking of \acp{NCS}, thanks to its low-cost, accessibility, and ease of reconfiguration.

Although the work of \textcite{Zoppi2020NCSBench} is a relevant and important step towards the reproducibility of \ac{NCS} benchmarks, we believe it still falls short on some aspects.
In particular, we argue the reliance of \emph{NCSbench} on specific hardware for the Plant hampers the potential of the platform.
The LEGO Mindstorms platform, although accessible and flexible, still fundamentally limits the physical systems that can be benchmarked to the kind of systems that can be physically implemented on it.
Furthermore, it is \emph{not} scalable, and thus unsuitable for studies of larger, distributed \acp{NCS}.

>>>>

The number and applications of \acp{CPS}~\cite{Rajkumar2010CPS} --- i.e.\ systems in which a real, physical mechanism is controlled by a computer --- have exploded in recent years.
However, this rapid increase in adoption has mostly been limited to industrial contexts.
Although \acp{CPS} present huge opportunities for all facets of society, they have yet to reach our daily lives in any relevant scale due to their stringent operational requirements.
This is about to change, however, as with the advent of novel wireless communication technologies as well as networking paradigms, such as cellular 5G and Edge Computing~\cite{Satya2017Emergence}, consumer-grade \acp{CPS} will be made possible.
These technologies meet two key requirements of \acp{CPS}: real-time capabilities (through extremely low end-to-end latencies), and context- and locality-awareness, and will most likely become the backbone of \ac{CPS} in the future.

@@

Due to their potential advantages for industrial and commercial settings, a large body of work exists dedicated to the modelling and performance characterization of \acp{NCS}~\cite{Zhang2013Survey,Zhang2016Survey}.
They improve and flexibilize existing control systems by allowing for the distribution of control functions over and across networks.
This allows for, e.g.\ centralized coordination, control, and monitoring of potentially hundreds of devices.

@@

One approach to experimental research in \acp{NCS} uses setups in which the complete system is built on top of real hardware.
This approach is employed in the works of, for instance, \textcite{Li2014Wireless,Baumann2018LowPower,Cuenca2019UAV}; in all of these, the authors implement and validate their results on physical testbeds.
Conversely, other studies choose to instead use completely \emph{simulated} \ac{NCS} setups.
\textcite{Wu2012NPC,Chen2015synccontrol,Ma2019DynamicSched} are examples of works in which the authors have opted for such completely virtualized approaches.
These studies often employ combinations of physical and network simulation tools to try to capture the complex dynamics of \acp{NCS}.
Finally, a number of experimental studies instead employ \emph{virtualized} approaches, in which either
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; or }}]
    \item a real network interacts with a simulated or emulated control system~\cite{Wang2020VoltageControl}
    \item an emulated or simulated network interacts with a real control system~\cite{Natale2004InvPendEthernet}.
\end{enumerate*}

As evidenced above, experimental research in \acp{NCS} includes a large variety of heterogeneous hardware and software platforms, as well as methodologies and \aclp*{KPI}.
This, in turn, leads to hardware, software, and methodology fragmentation, as different studies tend to prefer approaches more favored in their respective communities.
Furthermore, existing studies tend to focus on individual aspects and components of a system, thus producing results which do not provide a complete image of the \ac{NCS}.
This has caused a gap in knowledge pertaining to the reproducibility and comparison of experimental studies on these systems.

\textcite{Zoppi2020NCSBench} made the first (and to the best of our knowledge, the only) attempt at tackling this challenge with their \emph{NCSbench} platform.
\emph{NCSbench} is an open-source \ac{NCS} benchmarking platform, built on top of the LEGO\textregistered{}\ Mindstorms EV3 Core Set\texttrademark{}\ platform, with stated goals of reproducibility and ease of use.
It achives this thanks to its low-cost, accessibility, and ease of reconfiguration.

Although \emph{NCSbench}~\cite{Zoppi2020NCSBench} is a relevant and important step towards the reproducibility of \ac{NCS} benchmarks, we believe it still falls short on some aspects.
In particular, we argue the reliance of the tool on specific hardware for the Plant hampers the potential of the platform.
The LEGO Mindstorms platform, although accessible and flexible, still fundamentally limits the physical systems that can be benchmarked to the kind of systems that can be physically implemented on it.
Furthermore, it is \emph{not} scalable, and thus unsuitable for studies of larger, distributed \acp{NCS}.
